---
title: "ASSIGNMENT 4"
author: Yakup Tezcan
output:
  pdf_document: default
  word_document: default
---

```{r setup, include=TRUE}
knitr::opts_chunk$set(echo = TRUE)
assn4 <- read.csv(file = "assignment.csv")
```
```{r}
## code to create psych_rank vector and add to dataframe

# IMPORTANT: this code assumes that your dataframe is called a4

# create empty vector of zeros called meanness
# with length equivalent to original vector TriPM_M
meanness <- rep(0, length(assn4$TriPM_M))
# overwrite zeros in meanness vector using
# logical operators to determine if TriPM_M is >20
# or <= 20
meanness[assn4$TriPM_M> 15] <- 1
meanness[assn4$TriPM_M<= 15] <- 0

# repeat process for boldness
boldness <- rep(0, length(assn4$TriPM_B))
boldness[assn4$TriPM_B> 23] <- 1
boldness[assn4$TriPM_B<= 23] <- 0

# repeat process for disinhibition
dis <- rep(0, length(assn4$TriPM_D))
dis[assn4$TriPM_D> 24] <- 1
dis[assn4$TriPM_D<= 24] <- 0

# create a 'psych_rank' vector that 'counts'
# the number of traits that are 'high' for each
# individual
psych_rank <- meanness + boldness + dis

# add the psych_rank variable to the a4 dataframe
assn4 <- data.frame(cbind(assn4, psych_rank))
```

**QUESTION 1**

**A**

We are going to use a hypothesis test for the study and we are going to focus on Psychopathy rank(psych_rank) to evaluate whether the same pattern
(Canada, Portugal, the UK, and the USA)is consistent for Polish students.

**B**

Null hypothesis($H_{0}$) = p = $p_{0}$

Alternative hypothesis($H_{a}$) = p < $p_{0}$ or p > $p_{0}$ or p $\ne$ $p_{0}$

The prevalence of psychopathy for Polish students will be larger than 0.045

Let p the proportion of students in Polish universities whose psych_rank are 2 or 3.

$H_{0}$: p = 0.045

$H_{a}$: p > 0.045

\newpage

**QUESTION 2**

**A**

We are going to use a hypothesis test for the study and we are going to focus on Psychopathy rank(psych_rank) to evaluate whether the same pattern
(Canada, Portugal, the UK, and the USA)is consistent for Polish students.

**B**

Null hypothesis($H_{0}$) = p = $p_{0}$

Alternative hypothesis($H_{a}$) = p < $p_{0}$ or p > $p_{0}$ or p $\ne$ $p_{0}$

The prevalence of psychopathy for Polish students will be larger than 0.045

Let p the proportion of students in Polish universities whose psych_rank are 2 or 3.

$H_{0}$: p = 0.045

$H_{a}$: p > 0.045

**C**

```{r}
table(assn4$psych_rank > 1)
length(assn4$psych_rank)
prop.test(x=36,n=390,p=0.045,alternative="greater",correct=TRUE)
```

**D**

The proportion of students in Polish universities who demonstrate  psychopathic personality traits(95% CI:0.06-0.12)
higher than that of the general adult population.(0.045)
(Z=4.38, p=5.812e-06, n=390)


